 

### 2020-11-30 doc/manuscript/tables_figures/tables.Rmd
minor update to hypothesis table

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("1. Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("2. Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("3. Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
